PODD Ontology Driven Database

### 2012-03-08 epncanberra2012/Podd-20120313.tex
final draft before todays presentation

\begin{itemize}
 \item Aim to test hypotheses in known, partially controlled, situations
\pause
 \item Contain many variables
\pause
 \item Experiment variables and results are noted and used in analysis.
\pause
 \item Analysed results are used to make conclusions, which are published.
\end{itemize}
\end{frame}

@@

\begin{itemize}
 \item Two dimensional structure
\pause
 \item Suit simple relationships
\pause
 \item Single table not ideal for entire experiment
\pause
 \item Not ideal for multiple different experiments
\end{itemize}
\end{frame}

@@

\begin{itemize}
 \item Ontologies allow different structures for different experiments without changing the underlying database schema
\pause
 \item PODD has basic constraints
\begin{enumerate}
 \item Each ontology must have exactly one Project
 \item Each node must be connected to the Project through a unique series of ``part\_of'' links
 \item Each node can reference other nodes using ``refers\_to'' links
\end{enumerate}
\pause
\item A single ontology can be used with different unique experiments if it is designed well
\end{itemize}
\end{frame}

@@

\begin{itemize}
 \item Projects can be published on completion, both in HTML and RDF
\pause
 \item Published projects designed to be immutable
\pause
 \item Each data item has a URI
\end{itemize}
\end{frame}

>>>>

\begin{itemize}
 \item Aim to test hypotheses in known, partially controlled, situations
\pause
 \item Contain many variables
\pause
 \item Experiment variables and results are noted and used in analysis
\pause
 \item Analysed results are used to make conclusions, which are then published
\end{itemize}
\end{frame}

@@

\begin{itemize}
 \item Two dimensional structure
\pause
 \item Suit simple relationships
\pause
 \item Single table not ideal for entire experiment
\pause
 \item Not ideal for multiple structurally different experiments
\end{itemize}
\end{frame}

@@

\begin{itemize}
 \item Different structures for different experiments without changing the database schema
\pause
 \item PODD has basic ontology constraints
\begin{enumerate}
 \item Each ontology must have exactly one Project
 \item Each node must be connected to the Project through a unique series of ``part\_of'' links
 \item Each node can reference other eligible nodes using ``refers\_to'' links
\end{enumerate}
\pause
\item A single ontology can be used with different experiments if it is designed well
\end{itemize}
\end{frame}

@@

\begin{itemize}
 \item Projects can be published on completion, both in HTML and RDF
\pause
 \item Published projects may be locked from future changes
\pause
 \item Each data item has a URI for references
\end{itemize}
\end{frame}
